New lower bounds for Schur and weak Schur numbers

### 2021-04-18 article/weakschur.tex
Suppression de quelques environnements remarque

\begin{remark}
This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers.
\end{remark}

\begin{remark}
This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), this formula does not give
new lower bounds.
\end{remark}

\begin{remark}
In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
\end{remark}

@@

\begin{remark}
\(\pi\) is the projection on the first line mentioned in the intuitive explanation.
\end{remark}

@@

\begin{remark}
In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
\end{remark}

@@

\begin{remark}
	Please note that the special color \(n\) is not necessarily the last color by order of appearance.
\end{remark}

@@

\begin{corollary}
The general lower bound for weak Schur numbers in function of both regular and weak Schur numbers can be seen as a particular
case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template.
\end{corollary}

\begin{remark}
Acutally, like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on 
the last row. The principle behind it is the same as in the analogous proposition for SF-templates. 
\end{remark}

@@

\begin{remark}
The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only an additive
constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
use this sophistications given that we could not even find good WSF-templates with 5 colors using a computer (here good
means better than those obtain by combining smaller templates).

@@

\par
To sum up, one can look for a generalised WSF-template that uses a special colouring for the tail and the first row, a
colouring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a colouring for all
the other rows and a special colouring for the last numbers (as previously explained for the improvement of the additive
constant of WSF-templates).
\end{remark}

>>>>

This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers. This formula includes
the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), this formula does not give new lower bounds.

\begin{remark}
The above inequality can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
\end{remark}

@@

\(\pi\) is the projection on the first line mentioned in the intuitive explanation.

@@

In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.

@@

Please note that the special color \(n\) is not necessarily the last color by order of appearance.

@@

The general lower bound for weak Schur numbers in function of both regular and weak Schur numbers can be seen as a particular
case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template. Acutally,
like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on 
the last row. The principle behind it is the same as in the analogous proposition for SF-templates.

@@

The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only an additive
constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
use this sophistications given that we could not even find good WSF-templates with 5 colors using a computer (here good
means better than those obtain by combining smaller templates).

@@

\par
To sum up, one can look for a generalised WSF-template that uses a special colouring for the tail and the first row, a
colouring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a colouring for all
the other rows and a special colouring for the last numbers (as previously explained for the improvement of the additive
constant of WSF-templates).
